Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2015-02-21 doc/GMP2015/revision_1/appendix_b.tex
Compiles with Elsevier format. Got rid of minor spacing errors. Converted tikz figures to eps. Aligned subfigures. Etc. It's looking good! Now to consider major changes.
Finished and submitted revision 1.

\section{Appendix B}
\label{sec:appendix:b}

\subsection{Open Problems}
\label{sec:futurework}

One open problem comes from Section \ref{sec:DRP}:
\begin{openproblem}
    Is there a lower complexity algorithm than \candrpcomplexityv to find the canonical DR-plan of isostatic 2D bar-joint graphs?
\end{openproblem}

@@

\begin{openproblem}
    For fixed $k$ we have polynomial time optimal DR-planning, recombination (modification) in the presence of $k$ overconstraints (Section \ref{sec:DRP}, optimal modification for decomposition {\sl OMD}$_k(G)$, when at most $k$ constraints are removed \ref{sec:recomb} and also optimal completion using at most $k\le 2$ constraints in the body-pin and triangle-multipin cases under a modified measure for optimizing the DR-plan \ref{sec:table}. However, $k$ appears in the exponent for the straightforward algorithms for these problems.
\end{openproblem}

>>>>

\section{Open Problems}
\label{sec:appendix:b}

% \subsection{Open Problems}
\label{sec:futurework}

One open problem comes from Section \ref{sec:DRP}:
\begin{openproblem}
    Is there a lower complexity algorithm than \candrpcomplexityv\ to find the canonical DR-plan of isostatic 2D bar-joint graphs?
\end{openproblem}

@@

\begin{openproblem}
    For fixed $k$ we have polynomial time optimal DR-planning, recombination (modification) in the presence of $k$ overconstraints \todo{(Section \ref{sec:DRP},} optimal modification for decomposition {\sl OMD}$_k(G)$, when at most $k$ constraints are removed \ref{sec:recomb} and also optimal completion using at most $k\le 2$ constraints in the body-pin and triangle-multipin cases under a modified measure for optimizing the DR-plan \ref{sec:table}. However, $k$ appears in the exponent for the straightforward algorithms for these problems.
\end{openproblem}

### 2015-02-21 doc/GMP2015/revision_1/appendix_defs.tex
Finished and submitted revision 1.

\section{Preliminaries}
\label{sec:prelim}
%
\subsection{Basics}
%
In this paper, a \dfn{geometric constraint system} is a multivariate polynomial (usually bilinear or quadratic) system $G(x,\delta)=0$, representing constraints with parameters $\delta$ between geometric primitives  in $\mathbb{R}^2$ represented collectively as $x\in \mathbb{R}^n$.
%
When the type of constraint (system) is fixed, the system is simply represented as $(G,\delta)$, where $G$ is the underlying constraint (hyper)graph $G = (V,E)$ with the vertices $V$ representing the geometric primitives in $\mathbb{R}^2$ and (hyper)edges $E$ representing the constraints, each with an associated parameter $\delta$.
%
For example, a \dfn{bar-joint system or linkage} $(G,\delta)$, is a graph $G=(V,E)$ with fixed length bars as edges, i.e. $\delta: E \rightarrow \mathbb{R}$; this represents the distance constraint system $\| x_u -x_v \|_2 = \delta_{u,v}$ for  $(u,v) \in E$, where $x_u \in \mathbb{R}^2$ represents the coordinates of $u\in V$.

@@

In this paper, we will consider 3 types of constraint systems: bar-joint as well as \dfn{pinned line-incidence} and \dfn{body-hyperpin}. In all of these cases, a Cartesian \dfn{realization} or \dfn{solution} $G(p)$ of $(G,\delta)$ is an assignment of coordinates or Euclidean transformations (poses), $p: V \rightarrow \mathbb{R}^2$ or $\mathbb{R}^3$, to the vertices of $G$ satisfying the constraints with parameters $\delta$, modulo orientation preserving isometries (Euclidean rigid body motions for distance constraint).

@@

Defining the combinatorial independence of a subset of edges $E'\subseteq E$ to be the generic independence of corresponding rows in the appropriate rigidity matrix of indeterminates, we obtain the \dfn{rigidity matroid} of a constraint (hyper)graph $G = (V,E)$.%The 2-dimensional {\em rigidity matroid} of a constraint (hyper)graph $G = (V,E)$ is a linear matroid  on $E$,
%where a subset of edges $E' \subseteq E$ is {\em independent} in the matroid,
%if the set of corresponding rows in the appropriate rigidity matrix of indeterminates are linearly independent.
There are various results on combinatorial characterization of independence and rigidity  and rigidity matroids for different types of graphs. For bar-joint rigidity matroid, the famous Laman's theorem \cite{laman1970graphs} states that the underlying graph is isostatic if and only if $|E| = 2|V|-3$ and $|E'| \le 2|V'|-3$ for every induced subgraph with at least 2 vertices. The result by Lovasz and Yemini \cite{lovasz1982generic}  shows that all 6-vertex-connected graphs are rigid in the plane. For bar-body rigidity matroid, Tay \cite{tay1976rigidity} proved that the underlying multigraph is isostatic if and only if it can be decomposed as $3$ edge disjoint spanning trees. White and Whiteley \cite{white1987algebraic} gave the same characterization using a different technique to study the algebraic-geometric conditions of genericity, called pure condition. Lee, Streinu and Theran \cite{lee2007graded} defined the \dfn{$(k,l)$-sparsity matroid}, where a hypergraph $G$ is called \dfn{$(k,l)$-sparse} if $|E'| \le k|V'| - l$ for any induced subgraph $(V',E')$ with at least 2 vertices, and \dfn{$(k,l)$-tight} if is $(k,l)$-sparse and $|E| = k|V| - l$. In general, given a $d$-uniform hypergraph, a $(k,l)$-sparsity condition is matroidal as long as $l \le dk-1$.

In this paper, a \dfn{qusecs} is any \dfn{independent} geometric constraint system of one of the 3 types mentioned above.

% \medskip\noindent
% \note In the remainder of this section and sections~\ref{sec:DRP} and \ref{sec:recomb} we only consider bar-joint qusecs and graphs. Relevant formal analogies for the other 2 types of qusecs and (hyper)graphs are given in the subsequent 2 sections on Applications.

\sidenote{In the remainder of this section and sections~\ref{sec:DRP} and \ref{sec:recomb} we only consider bar-joint qusecs and graphs. Relevant formal analogies for the other 2 types of qusecs and (hyper)graphs are given in the subsequent 2 sections on Applications.}

@@

The notation $Idc(G,X)$ is the subgraph of $G$ induced by the vertex set $X\subseteq V$. For a subgraph $H=(W,F)$ of $G$, $Idc(G,H)=Idc(G,W)$.

\subsection{Decomposition-Recombination (DR) Plans}
%
%$G=(V,E,w_V,w_E)$ is a set of vertices, $V$, and a set of edges, $E$, defined as a tuple of vertices from $V$ (undirected). Additionally, there are two weight functions, $w_V: V \to \mathbb{R}^+$ and $w_E: E \to \mathbb{R}^+$. The \textbf{density} of graph $G$ is $d(G) = \sum_{e\in E}{w_E(e)} - \sum_{v\in V}{w_V(v)}$.
%
%Given a constant $k$, a graph $G$ is:
%\begin{itemize}
%    \item \textbf{independent} (or \textbf{sparse}) if, for all non-trivial subgraphs $S\subseteq G$, $d(S) \leq k$.
%
%    \item \textbf{overconstrained} if it is not independent.
%
%    \item \textbf{wellconstrained} (or \textbf{tight}) if $G$ is independent and $d(G)=k$.
%
%    \item \textbf{rigid} if there exists some spanning subgraph $S\subseteq G$ such that $S$ is wellconstrained.
%
%    \item \textbf{underconstrained} if $G$ is independent and not rigid.
%
%    % \item \textbf{trivial} if (1) it is overconstrained graph and (2) all of its subgraphs are also trivial. Trivial graphs are input.
%\end{itemize}
%
% \begin{definition}
%     A graph is \textbf{overconstrained} if, given constant $k$, there exists some
%     % induced
%     subgraph $S\subseteq G$ such that $d(S) > k$.
% \end{definition}
%
% \begin{definition}
%     A graph is \textbf{wellconstrained} if, given constant $k$, $d(G) = k$ and for all
%     % induced
%     subgraphs $S\subseteq G$, (1) $d(S)\leq k$, or (2) given a set of trivial graphs $T$, $S$ is isomorphic to one of the graphs in $T$ (i.e.\ $S$ is trivial).
% \end{definition}
%
%
%
% \begin{definition}
%     A \textbf{trivial} graph is ill-defined in the general case. The only strict requirements are: (1) it must be an overconstrained graph and (2) all of its subgraphs are also trivial.
%     \todo{Maybe leave the following out until it's needed later?}
%     In the familiar geometric cases of $d$-dimensional space, all vertex weights are $d$, all edge weights are $1$, and constant $k= -{{d+1}\choose{2}}$. Trivial graphs for 2D would be a single vertex. Trivial graphs in 3D would be a vertex and an edge (2 vertices with an edge between). Etc. These trivial graphs capture the notion of the rotational symmetry that exists in geometric spaces.
% \end{definition}
%
\begin{definition}\label{def:drp}
    The \dfn{decomposition-recombination \mbox{(DR-)} plan} of graph $G$, \cite{hoffman2001decompositionI} $\drp{G}$ (see Figure \ref{fig:c2c3ofk33s}, is defined as a forest that has the following properties:
    \begin{enumerate}
        \item Each node represents/contains/is a rigid vertex-induced subgraph of $G$.
        % \item For a node, $C$, that is  a non-trivial graph, its $N$
        % children, $C_1, \ldots, C_N$, are rigid vertex-maximal proper
        % subgraphs of $C$.
        \item Node $C$ has children $C_1,\ldots,C_N$ such that $\bigcup_{i=1}^N{C_i}=C$.
        \item A leaf node is a single vertex. A \dfn{trivial} graph is empty or a single vertex.
        \item A root node is a maximal rigid subgraph of $G$.
    \end{enumerate}
%
    % It can also be described recursively as: the root is $G$, its children are the trivial subgraphs and the DR-plans of its wellconstrained vertex-maximal proper subgraphs whose union is $G$ itself.
%
    A DR-plan is \dfn{complete} if it satisfies an additional rule:
        \item For a node $C$ that is  a non-trivial graph, its $N$ children, $C_1, \ldots, C_N$, are all of the rigid vertex-maximal proper subgraphs of $C$. This makes Rule 2 implicit, and in fact, $C$ contains all the edges in the union of its children as well. We denote a complete DR-plan of $G$ as $\comdrp{G}$
    A DR-plan is \dfn{optimal} if it minimizes the maximum fan-in over all nodes in the tree. The maximum  fan-in is called the \dfn{size} of the DR-plan. We denote an optimal DR-plan of $G$ as $\optdrp{G}$.

%
%In general, $C$ is the graph in an arbitrary node in $CompleteDRP(G)$.
%$C_i$ is the $i^{\text{th}}$ child of $C$. It is implied that $C_i$ is
%an isostatic vertex-maximal proper subgraph.
    %Note that nodes will be referred to interchangeably as ``the node that
    %represents or contains the (sub)graph $C$'' and as simply ``$C$''.
\end{definition}
%
% \todo{This was labeled as both begin(remark) and end(observation), what was your intent?}
\begin{remark}
    For a given graph, there could be exponentially many  DR-plans and even optimal DR-plans in the size of the graph. A complete DR-plan is unique but may not be (is usually not) optimal. DR-plans of self-similar graphs are self-similar. More than one node (leaf) in a DR-plan forest may represent the same subgraph (vertex) of $G$.
\end{remark}

% \begin{definition}
%     The \textbf{complete DR-plan} of graph $G$, $CompleteDRP(G)$, is the unique DR-plan but with a modified rule number 2: the children are \emph{all} of the trivial or wellconstrained vertex-maximal proper subgraphs of that node $C$. By this, rule 3 is implicit for a complete DR-plan.
% \end{definition}

% \begin{definition}
%     The \textbf{optimal DR-plan} of graph $G$, $OptimalDRP(G)$, is the DR-plan that minimizes the maximum fan-in over all nodes in the tree. It is not necessarily unique.
% \end{definition}

%\emph{wellconstrained} bar and joint graph with values $(V,E,w_V,w_E)$.
% \todo{I don't think the following is actually necessary to mention...} To keep problems meaningful we assume that $G$ is connected, as the methods discussed are used to solve systems of equations to establish linkages. It is not useful to solve for two bodies simultaneously if there are no constraints between them.
% THIS MEANS NO EDGES MAY BE LEFT OUT, ALSO.

\sidenote{In Section \ref{sec:DRP}, $G$ is assumed to be isostatic.}

\subsection{Importance of an Optimal DR-plan}
The use of a DR-plan in designing especially self-similar qusecs is immediately evident, shown in Figures \ref{fig:c2c3ofk33s} and \ref{fig:subdivision}.

In fact, knowing an optimal DR-plan is crucial for design and analysis of even non-self-similar qusecs and their realizations with various desirable properties.

\medskip\noindent
\header{Realizing given qusecs.}
Note that this basic task would require finding real solutions a large multivariate polynomial system (of inequalities and equalities representing the constraints). Without DR-planning, this requires double exponential time in the number of variables (even if orientation type is specified). With DR-planning, the complexity is dominated by the size of the largest subsystem that is solved, or recombined from the solutions of its child subsystems i.e.,the maximum fan-in occurring in a DR-plan. Thus finding an optimal DR-plan is important for realization.

\medskip\noindent
\header{Recursive block decomposition of the rigidity matrix, stress space and external stresses.}
This can be obtained using the DR-plan we obtain a with each block being the rigidity matrix of an isostatic subgraph. The blocks intersect on isostatic or trivial subgraphs. This recursive block decomposition of the rigidity matrix $R$ correspondingly recursively decomposes the stress vectors $s$ that balance a given external stress $t$ since $sR = t$. Moreover, the external stress vector $t$ is recursively ``distributed'' into external stresses for each node of the DR-plan. When the rigidity matrix and stress vectors contain indeterminates, this  can be used to design underlying graph and parameters $\delta$ to obtain an optimal distribution of stresses on the geometric primitives. When the realization of qusecs is given, this can be used to analyze the distribution of a given external load.

%\subsection{DR-plan}
%%\subsection{Definitions}
%%\label{sec:prelim_defs}
%%
%%% TODO
%%
%%% A paragraph of preliminaries such as:
%%%     - rigidity matrix R,
%%%     - stress vectors S one coordinate per edge (w/ SR =E (external stress vector, 2 coordinates  per vertex));
%%%     - flex vectors F (2 coordinates per vertex) (right nullspace/kernel of R)
%%% Should precede the definition of
%%%     + independent,
%%%     + overconstrained (not independent),
%%%     - rigid (contains an independent set with sufficiently many eedges/constraints)
%%%     - isostatic (wellconstrained/minimally rigid), ,
%%%     - flexible (not rigid),
%%%     + underconstrained (independent and not rigid).
%%% After that, define DR plans etc.
%%
%%In Sections \ref{sec:DRP} and \ref{sec:recomb} a \textbf{graph} is a bar and joint system. $G=(V,E,w_V,w_E)$ is a set of vertices, $V$, and a set of edges, $E$, defined as a tuple of vertices from $V$ (undirected). Additionally, there are two weight functions, $w_V: V \to \mathbb{R}^+$ and $w_E: E \to \mathbb{R}^+$. The \textbf{density} of graph $G$ is $d(G) = \sum_{e\in E}{w_E(e)} - \sum_{v\in V}{w_V(v)}$.
%%
%%Given a constant $k$, a graph $G$ is:
%%\begin{itemize}
%%    \item \textbf{independent} (or \textbf{sparse}) if, for all non-trivial subgraphs $S\subseteq G$, $d(S) \leq k$.
%%
%%    \item \textbf{overconstrained} if it is not independent.
%%
%%    \item \textbf{wellconstrained} (or \textbf{tight}) if $G$ is independent and $d(G)=k$.
%%
%%    \item \textbf{rigid} if there exists some spanning subgraph $S\subseteq G$ such that $S$ is wellconstrained.
%%
%%    \item \textbf{underconstrained} if $G$ is independent and not rigid.
%%
%%    % \item \textbf{trivial} if (1) it is overconstrained graph and (2) all of its subgraphs are also trivial. Trivial graphs are input.
%%\end{itemize}
%%
%\textbf{Trivial} graphs are ill-defined in the general case. The only strict requirements are: (1) it must overconstrained and (2) all of its subgraphs are also trivial.
%
%% \begin{definition}
%%     A graph is \textbf{overconstrained} if, given constant $k$, there exists some
%%     % induced
%%     subgraph $S\subseteq G$ such that $d(S) > k$.
%% \end{definition}
%
%% \begin{definition}
%%     A graph is \textbf{wellconstrained} if, given constant $k$, $d(G) = k$ and for all
%%     % induced
%%     subgraphs $S\subseteq G$, (1) $d(S)\leq k$, or (2) given a set of trivial graphs $T$, $S$ is isomorphic to one of the graphs in $T$ (i.e.\ $S$ is trivial).
%% \end{definition}
%
%
%
%% \begin{definition}
%%     A \textbf{trivial} graph is ill-defined in the general case. The only strict requirements are: (1) it must be an overconstrained graph and (2) all of its subgraphs are also trivial.
%%     \todo{Maybe leave the following out until it's needed later?}
%%     In the familiar geometric cases of $d$-dimensional space, all vertex weights are $d$, all edge weights are $1$, and constant $k= -{{d+1}\choose{2}}$. Trivial graphs for 2D would be a single vertex. Trivial graphs in 3D would be a vertex and an edge (2 vertices with an edge between). Etc. These trivial graphs capture the notion of the rotational symmetry that exists in geometric spaces.
%% \end{definition}
%
%
%\begin{definition}\label{def:drp}
%    The \textbf{decomposition-recombination \mbox{(DR-)} plan} of graph $G$, $DRP(G)$, is defined as a tree that has the following properties:
%    \begin{enumerate}
%        \item The root of the tree `contains' $G$.
%        \item For all nodes, $C$, that `contain' non-trivial graphs, its $N$ children, $C_1, \ldots, C_N$, are trivial or wellconstrained vertex-maximal proper subgraphs of that node $C$.
%        \item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
%        \item A node with a trivial subgraph is a leaf.
%    \end{enumerate}
%
%    % It can also be described recursively as: the root is $G$, its children are the trivial subgraphs and the DR-plans of its wellconstrained vertex-maximal proper subgraphs whose union is $G$ itself.
%
%    An equivalent DAG can be constructed from this tree such that all nodes containing the same subgraphs are combined into one, with all edges preserved.
%
%    Note that nodes will be referred to interchangeably as ``the node that contains the (sub)graph $C$'' and as simply ``$C$''.
%
%    A DR-plan is \textbf{complete} if it satisfies the modified rule number 2: the children are \emph{all} of the trivial or wellconstrained vertex-maximal proper subgraphs of that node $C$. This makes rule 3 implicit. The complete DR-plan is unique.
%
%    A DR-plan is \textbf{optimal} if it minimizes the maximum fan-in over all nodes in the tree. It is not necessarily unique.
%\end{definition}
%
%% \begin{definition}
%%     The \textbf{complete DR-plan} of graph $G$, $CompleteDRP(G)$, is the unique DR-plan but with a modified rule number 2: the children are \emph{all} of the trivial or wellconstrained vertex-maximal proper subgraphs of that node $C$. By this, rule 3 is implicit for a complete DR-plan.
%% \end{definition}
%
%% \begin{definition}
%%     The \textbf{optimal DR-plan} of graph $G$, $OptimalDRP(G)$, is the DR-plan that minimizes the maximum fan-in over all nodes in the tree. It is not necessarily unique.
%% \end{definition}
%
%
%\subsection{Notation}
%
%In Sections \ref{sec:DRP} and \ref{sec:recomb}, $G$ is taken to be a \emph{wellconstrained} bar and joint graph with values $(V,E,w_V,w_E)$.
%% \todo{I don't think the following is actually necessary to mention...} To keep problems meaningful we assume that $G$ is connected, as the methods discussed are used to solve systems of equations to establish linkages. It is not useful to solve for two bodies simultaneously if there are no constraints between them.
%% THIS MEANS NO EDGES MAY BE LEFT OUT, ALSO.
%
%$Idc(G,X)$ is the graph induced on $G$ with the vertex set $X\subseteq V$. This can also be overloaded such that, using graph $H=(W,F)$, $Idc(G,H)=Idc(G,W)$.
%
%$C$ is the graph in an arbitrary node in $CompleteDRP(G)$. $C_i$ is the $i^{\text{th}}$ child of $C$. By definition of a DR-plan, it is implied that $C_i$ is a wellconstrained vertex-maximal proper subgraph.

>>>>

\section{Basic Definitions and Theory}
\label{sec:appendix:defs}

\notetoreviewer{The following section was moved in from the Preliminaries section.}

In this paper, a \dfn{geometric constraint system} is a multivariate polynomial (usually bilinear or quadratic) system $G(x,\delta)=0$, representing constraints with parameters $\delta$ between geometric primitives  in $\mathbb{R}^2$ represented collectively as $x\in \mathbb{R}^n$.
%
When the type of constraint (system) is fixed, the system is simply represented as $(G,\delta)$, where $G$ is the underlying constraint (hyper)graph $G = (V,E)$ with the vertices $V$ representing the geometric primitives in $\mathbb{R}^2$ and (hyper)edges $E$ representing the constraints, each with an associated parameter $\delta$.
%
For example, a \dfn{bar-joint system or linkage} $(G,\delta)$, is a graph $G=(V,E)$ with fixed length bars as edges, i.e. $\delta: E \rightarrow \mathbb{R}$; this represents the distance constraint system $\| x_u -x_v \|_2 = \delta_{u,v}$ for  $(u,v) \in E$, where $x_u \in \mathbb{R}^2$ represents the coordinates of $u\in V$.

@@

In this paper, we will consider 3 types of constraint systems: bar-joint as well as \dfn{body-hyperpin} \addin{(defined formally in Section \ref{sec:bodypin})} and \dfn{pinned line-incidence} \addin{(defined formally in Section \ref{sec:pinnedline})}. In all of these cases, a Cartesian \dfn{realization} or \dfn{solution} $G(p)$ of $(G,\delta)$ is an assignment of coordinates or Euclidean transformations (poses), $p: V \rightarrow \mathbb{R}^2$ or $\mathbb{R}^3$, to the vertices of $G$ satisfying the constraints with parameters $\delta$, modulo orientation preserving isometries (Euclidean rigid body motions for distance constraint).

@@

Defining the combinatorial independence of a subset of edges $E'\subseteq E$ to be the generic independence of corresponding rows in the appropriate rigidity matrix of indeterminates, we obtain the \dfn{rigidity matroid} of a constraint (hyper)graph $G = (V,E)$.
%The 2-dimensional {\em rigidity matroid} of a constraint (hyper)graph $G = (V,E)$ is a linear matroid  on $E$,
%where a subset of edges $E' \subseteq E$ is {\em independent} in the matroid,
%if the set of corresponding rows in the appropriate rigidity matrix of indeterminates are linearly independent.
There are various results on combinatorial characterization of independence and rigidity  and rigidity matroids for different types of graphs. For bar-joint rigidity matroid, the famous Laman's theorem \cite{laman1970graphs} states that the underlying graph is isostatic if and only if $|E| = 2|V|-3$ and $|E'| \le 2|V'|-3$ for every induced subgraph with at least 2 vertices. The result by Lovasz and Yemini \cite{lovasz1982generic}  shows that all 6-vertex-connected graphs are rigid in the plane. For bar-body rigidity matroid, Tay \cite{tay1976rigidity} proved that the underlying multigraph is isostatic if and only if it can be decomposed as $3$ edge disjoint spanning trees. White and Whiteley \cite{white1987algebraic} gave the same characterization using a different technique to study the algebraic-geometric conditions of genericity, called pure condition. Lee, Streinu and Theran \cite{lee2007graded} defined the \dfn{$(k,l)$-sparsity matroid}, where a hypergraph $G$ is called \dfn{$(k,l)$-sparse} if $|E'| \le k|V'| - l$ for any induced subgraph $(V',E')$ with at least 2 vertices, and \dfn{$(k,l)$-tight} if is $(k,l)$-sparse and $|E| = k|V| - l$. In general, given a $d$-uniform hypergraph, a $(k,l)$-sparsity condition is matroidal as long as $l \le dk-1$.

\cutout{In this paper, a qusecs is any independent geometric constraint system of one of the 3 types mentioned above.} \notetoreviewer{This now only in the Preliminaries section.}

% In this paper, a \dfn{qusecs} is any \dfn{independent} geometric constraint system of one of the 3 types mentioned above.

% % \medskip\noindent
% % \note In the remainder of this section and sections~\ref{sec:DRP} and \ref{sec:recomb} we only consider bar-joint qusecs and graphs. Relevant formal analogies for the other 2 types of qusecs and (hyper)graphs are given in the subsequent 2 sections on Applications.

% \sidenote{In the remainder of this section and Sections~\ref{sec:DRP} and \ref{sec:recomb} we only consider bar-joint qusecs and graphs. Relevant formal analogies for the other 2 types of qusecs and (hyper)graphs are given in the subsequent 2 sections on Applications (\ref{sec:bodypin} and \ref{sec:pinnedline}).}

@@
